assessment

### 2018-08-13 manuscript/supplementary_notes/metrics/assessment.Rmd
update to metric characterisation

```{r}
width <- ifelse(is.null(assessment$plot_datasets$width), 1, assessment$plot_datasets$width)
height <- ifelse(is.null(assessment$plot_datasets$height), 1, assessment$plot_datasets$height)
```
```{r A, fig.width=width, fig.height=height, out.width=paste0(width/2, "in")}
assessment$plot_datasets
```

```{r}
width <- ifelse(is.null(assessment$plot_scores$width), 1, assessment$plot_scores$width)
height <- ifelse(is.null(assessment$plot_scores$height), 1, assessment$plot_scores$height)
```
```{r B, fig.width=width, fig.height=height, out.width=paste0(width/2, "in")}
assessment$plot_scores
```

>>>>

`r rule$observation`

```{r}
width <- ifelse(is.null(assessment$plot_datasets$width), 10, assessment$plot_datasets$width)
height <- ifelse(is.null(assessment$plot_datasets$height), 10, assessment$plot_datasets$height)
```
```{r A, fig.width=width, fig.height=height, out.width=paste0(width/2, "in")}
assessment$plot_datasets
```

```{r}
width <- ifelse(is.null(assessment$plot_scores$width), 10, assessment$plot_scores$width)
height <- ifelse(is.null(assessment$plot_scores$height), 10, assessment$plot_scores$height)
```
```{r B, fig.width=width, fig.height=height, out.width=paste0(width/2, "in")}
assessment$plot_scores
```
